---
title: "Data624_Assignment2"
author: "Ritesh Lohiya"
date: "February 14, 2019"
output: html_document
---

#Data624 The forecaster's toolbox Assignment2

#Chapter 3:

```{r}
suppressMessages(suppressWarnings(library(fpp2)))
suppressMessages(suppressWarnings(library(readxl)))
```

#3.1 For the following series, find an appropriate Box-Cox transformation in order to stabilise the variance.

#usnetelec:

```{r}
lmd = BoxCox.lambda(usnetelec)
lmd  
usnetelec.trans = BoxCox(usnetelec,lmd)
combined = cbind(usnetelec,usnetelec.trans)
autoplot(combined,facet=T) + xlab("Year") + ggtitle("usnetelec")
```

#usgdp:

```{r}
lmd = BoxCox.lambda(usgdp)
lmd  
usgdp.trans = BoxCox(usgdp,lmd)
combined = cbind(usgdp,usgdp.trans)
autoplot(combined,facet=T) + xlab("Year") + ggtitle("usgdp")
```

#mcopper:

```{r}
lmd = BoxCox.lambda(mcopper)
lmd  
mcopper.trans = BoxCox(mcopper,lmd)
combined = cbind(mcopper,mcopper.trans)
autoplot(combined,facet=T) + xlab("Year") + ggtitle("mcopper")
```

#enplanements:

```{r}
lmd = BoxCox.lambda(enplanements)
lmd  
enplanements.trans = BoxCox(enplanements,lmd)
combined = cbind(enplanements,enplanements.trans)
autoplot(combined,facet=T) + xlab("Year") + ggtitle("enplanements")
```

#3.2 Why is a Box-Cox transformation unhelpful for the cangas data?

#To answer this lets first autoplot the cangas data.

#cangas:

```{r}
lmd = BoxCox.lambda(cangas)
lmd  
cangas.trans = BoxCox(cangas,lmd)
combined = cbind(cangas,cangas.trans)
autoplot(combined,facet=T) + xlab("Year") + ggtitle("cangas")
```

#This time series is monthly Canadian gas production, in billions of cubic metres, January 1960 - February 2005. There is not much variations in the plots. So transformation is not always needed. 


#3.3 What Box-Cox transformation would you select for your retail data (from Exercise 3 in Section 2.10)?

Retails data:

```{r}
retaildata <- readxl::read_excel("C:/Users/rites/Documents/GitHub/Data624_Assignment1/retail.xlsx", skip=1)
myts <- ts(retaildata[,"A3349873A"],frequency=12, start=c(1982,4))
```

```{r}
lmd = BoxCox.lambda(myts)
lmd  
myts.trans = BoxCox(myts,lmd)
combined = cbind(myts,myts.trans)
autoplot(combined,facet=T) + xlab("Year") + ggtitle("myts")
```

#It would be good to choose Box-Cox Transformation with lambda = 0.1276369


#3.8 For your retail time series (from Exercise 3 in Section 2.10):

#a. Split the data into two parts using

```{r}
myts.train <- window(myts, end=c(2010,12))
myts.test <- window(myts, start=2011)
```

#b. Check that your data have been split appropriately by producing the following plot.

```{r}
autoplot(myts) +
autolayer(myts.train, series="Training") +
autolayer(myts.test, series="Test")
```

#c. Calculate forecasts using snaive applied to myts.train.

```{r}
fc <- snaive(myts.train)
```

#d. Compare the accuracy of your forecasts against the actual values stored in myts.test.

```{r}
accuracy(fc,myts.test)
```

#e. Check the residuals.

```{r}
checkresiduals(fc)
```

#Do the residuals appear to be uncorrelated and normally distributed?

#Residuals are correlated with each other and not normally distributed

#f. How sensitive are the accuracy measures to the training/test split?

#Sensitivity is the ratio of the test set error to the train set error. Looking at the accuracy results, i feel accuracy measures are very sensitive to training/test split.

